\section*{NeurIPS Paper Checklist}

\begin{enumerate}[leftmargin=*]
\item \textbf{Claims}
\item[] Question: Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
\item[] Answer: \answerYes{}
\item[] Justification: The abstract and Section~1 state the core claims precisely: direct Flash-style transfer fails on BAGEL, and UQP-Bagel improves both generation and understanding under explicit quality constraints.

\item \textbf{Limitations}
\item[] Question: Does the paper discuss the limitations of the work performed by the authors?
\item[] Answer: \answerYes{}
\item[] Justification: Section~7 explicitly discusses pilot-scale evaluation, the oracle-style planner, imperfect quality proxies, and the lack of error bars.

\item \textbf{Theory assumptions and proofs}
\item[] Question: For each theoretical result, does the paper provide the full set of assumptions and a complete (and correct) proof?
\item[] Answer: \answerNA{}
\item[] Justification: The paper does not claim a formal theorem or proof; its contribution is a training-free systems-and-method formulation supported by empirical evidence.

\item \textbf{Experimental result reproducibility}
\item[] Question: Does the paper fully disclose all the information needed to reproduce the main experimental results of the paper to the extent that it affects the main claims and/or conclusions of the paper (regardless of whether the code and data are provided or not)?
\item[] Answer: \answerYes{}
\item[] Justification: Sections~4--6 and Appendix~A describe the model, candidate paths, quality constraints, hardware, and the exact aggregated CSV assets used in the paper.

\item \textbf{Open access to data and code}
\item[] Question: Does the paper provide open access to the data and code, with sufficient instructions to faithfully reproduce the main experimental results, as described in supplemental material?
\item[] Answer: \answerNo{}
\item[] Justification: The submission package describes the code and data layout and includes derived CSV assets, but an anonymized public release of the evaluation code and scripts has not yet been attached to this draft.

\item \textbf{Experimental setting/details}
\item[] Question: Does the paper specify all the training and test details (e.g., data splits, hyperparameters, how they were chosen, type of optimizer) necessary to understand the results?
\item[] Answer: \answerYes{}
\item[] Justification: The paper is training-free. Section~4 and Appendix~A specify the candidate schedules, understanding budgets, prompt suite, hardware, and measured metrics needed to interpret the results.

\item \textbf{Experiment statistical significance}
\item[] Question: Does the paper report error bars suitably and correctly defined or other appropriate information about the statistical significance of the experiments?
\item[] Answer: \answerNo{}
\item[] Justification: The current evaluation is a deterministic pilot study over five generation prompts and ten understanding items, so we report exact averages but not repeated-run error bars or confidence intervals.

\item \textbf{Experiments compute resources}
\item[] Question: For each experiment, does the paper provide sufficient information on the computer resources (type of compute workers, memory, time of execution) needed to reproduce the experiments?
\item[] Answer: \answerYes{}
\item[] Justification: Section~5 states that all experiments were run on the same remote Linux server with a single NVIDIA RTX PRO 6000 Blackwell Server Edition GPU and reports wall-clock runtimes for all compared systems.

\item \textbf{Code of ethics}
\item[] Question: Does the research conducted in the paper conform, in every respect, with the NeurIPS Code of Ethics https://neurips.cc/public/EthicsGuidelines?
\item[] Answer: \answerYes{}
\item[] Justification: The paper studies inference efficiency on an existing model family, preserves anonymity, and does not involve deceptive reporting, human subjects, or hidden data collection.

\item \textbf{Broader impacts}
\item[] Question: Does the paper discuss both potential positive societal impacts and negative societal impacts of the work performed?
\item[] Answer: \answerYes{}
\item[] Justification: Section~7 discusses both positive effects of cheaper multimodal deployment and negative risks associated with making generative systems cheaper to run.

\item \textbf{Safeguards}
\item[] Question: Does the paper describe safeguards that have been put in place for responsible release of data or models that have a high risk for misuse (e.g., pre-trained language models, image generators, or scraped datasets)?
\item[] Answer: \answerNA{}
\item[] Justification: The paper does not release new model weights or a new scraped dataset; it reports aggregated metrics and qualitative examples from an existing model release.

\item \textbf{Licenses for existing assets}
\item[] Question: Are the creators or original owners of assets (e.g., code, data, models), used in the paper, properly credited and are the license and terms of use explicitly mentioned and properly respected?
\item[] Answer: \answerNo{}
\item[] Justification: The paper credits BAGEL and the compared acceleration methods, but the anonymized draft does not enumerate the exact license strings and terms-of-use text for every upstream asset.

\item \textbf{New assets}
\item[] Question: Are new assets introduced in the paper well documented and is the documentation provided alongside the assets?
\item[] Answer: \answerYes{}
\item[] Justification: The new assets are the planner description, aggregated CSV summaries, and qualitative contact sheets; Appendix~A documents their role and the output package layout.

\item \textbf{Crowdsourcing and research with human subjects}
\item[] Question: For crowdsourcing experiments and research with human subjects, does the paper include the full text of instructions given to participants and screenshots, if applicable, as well as details about compensation (if any)?
\item[] Answer: \answerNA{}
\item[] Justification: The paper does not involve crowdsourcing or human-subject experiments.

\item \textbf{Institutional review board (IRB) approvals or equivalent for research with human subjects}
\item[] Question: Does the paper describe potential risks incurred by study participants, whether such risks were disclosed to the subjects, and whether Institutional Review Board (IRB) approvals (or an equivalent approval/review based on the requirements of your country or institution) were obtained?
\item[] Answer: \answerNA{}
\item[] Justification: The paper does not involve human subjects.

\item \textbf{Declaration of LLM usage}
\item[] Question: Does the paper describe the usage of LLMs if it is an important, original, or non-standard component of the core methods in this research? Note that if the LLM is used only for writing, editing, or formatting purposes and does \emph{not} impact the core methodology, scientific rigor, or originality of the research, declaration is not required.
\item[] Answer: \answerNA{}
\item[] Justification: LLMs are not part of the core experimental method or scientific claims in this paper.
\end{enumerate}
